A Bayesian Perspective \\\large{Extracorporeal CPR for Refractory Out-of-Hospital Cardiac Arrest}

### 2023-02-12 manuscript/manuscript.qmd
bayesian guideline reporting

Posterior distributions were estimated using the Hamiltonian Monte Carlo,a form of 
Markov Chain Monte Carlo simulations in which the gradient of the log posterior is 
used to efficiently sample the posterior space. This was implemented in `Stan`[@stan] using the front end `rstanarm` package[@rstanarm] by fitting a logistic regression model with a single treatment parameter. All analyses were executed using `R`[@R]  within the integrated development environmentof RStudio[@Rstudio].  Model convergence was assessed by examination of the Monte Carlo Standard Error < 10% of the posterior standard deviation, $n_{eff}$ an estimate of the effective number of independent draws from the posterior distribution of the estimand > 10% maximum and $\hat{R}$  a measures the ratio of the average variance of samples within each chain to the variance of the pooled samples across chains < 1.1. The statistical code can be found on Github
(https://github.com/brophyj/eCPR).

@@

# - INCEPTION alone default vague priors
set.seed(1234)
fit1 <- stan_glm(prop_success ~ Tx, data = df[c(1:2),], family = binomial(link="logit"), weights = total, refresh=0) #stan_glm with combined prior
fit1_sum <- summary(fit1, digits=3) # check convergence
conf_95 <- c(exp(fit1_sum[2]),exp(fit1_sum[2]+c(-1,1)*1.96*fit1_sum[10]))
tt <- fit1 %>%
    spread_draws(`(Intercept)`, `TxeCPR`)
fig_prob <- sum(tt$TxeCPR>0)/nrow(tt)
# summary(fit1, digits=3)
# print(c(exp(.2785),exp(.2785+c(-1,1)*1.96*.4537)))
# get_variables(fit1)
# prior_summary(fit1)
# help('prior_summary.stanreg') 
# plot(fit1)
# P > 1.1
fig_prob_1.1 <- sum(tt$TxeCPR > 0.0953)/nrow(tt) # OR >1.1 (log (1.1) = 0.0953)
# [1] 0.657

>>>>

Posterior distributions were estimated using the Hamiltonian Monte Carlo,a form of 
Markov Chain Monte Carlo simulations in which the gradient of the log posterior is 
used to efficiently sample the posterior space. This was implemented in `Stan`[@stan] using the front end `rstanarm` package[@rstanarm] by fitting a logistic regression model with a single treatment parameter. All analyses were executed using `R`[@R]  within the integrated development environmentof RStudio[@Rstudio].  Model convergence was assessed by examination of the Monte Carlo Standard Error < 10% of the posterior standard deviation, $n_{eff}$ an estimate of the effective number of independent draws from the posterior distribution of the estimand > 10% maximum and $\hat{R}$  a measures the ratio of the average variance of samples within each chain to the variance of the pooled samples across chains < 1.1. Reporting has followed the Bayesian Analysis Reporting Guidelines[@RN6637]. The statistical code can be found on Github
(https://github.com/brophyj/eCPR).

@@

# - INCEPTION alone default vague priors
set.seed(1234)
fit1 <- stan_glm(prop_success ~ Tx, data = df[c(1:2),], family = binomial(link="logit"), weights = total, refresh=0) #stan_glm with combined prior
fit1_sum <- summary(fit1, digits=3) # check convergence
conf_95 <- c(exp(fit1_sum[2]),exp(fit1_sum[2]+c(-1,1)*1.96*fit1_sum[10]))
tt <- fit1 %>%
    spread_draws(`(Intercept)`, `TxeCPR`)
fig_prob <- sum(tt$TxeCPR>0)/nrow(tt)
# summary(fit1, digits=3)
# print(c(exp(.2785),exp(.2785+c(-1,1)*1.96*.4537)))
# get_variables(fit1)
# prior_summary(fit1)
# help('prior_summary.stanreg') 
# mcmc_pairs(as.array(fit1),  pars = c("(Intercept)",  "TxeCPR" ),off_diag_args = list(size = 0.75))
# mcmc_trace(fit1)
# plot(fit1)
# P > 1.1
fig_prob_1.1 <- sum(tt$TxeCPR > 0.0953)/nrow(tt) # OR >1.1 (log (1.1) = 0.0953)
# [1] 0.657

### 2023-02-12 manuscript/manuscript.tex
bayesian guideline reporting

\begin{keyword}
    extracorporeal CPR \sep 
    Bayesian statistics
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, enhanced, frame hidden, interior hidden, breakable, borderline west={3pt}{0pt}{shadecolor}, sharp corners]}{\end{tcolorbox}}\fi

@@

Posterior distributions were estimated using the Hamiltonian Monte
Carlo,a form of Markov Chain Monte Carlo simulations in which the
gradient of the log posterior is used to efficiently sample the
posterior space. This was implemented in \texttt{Stan}\citep{stan} using
the front end \texttt{rstanarm} package\citep{rstanarm} by fitting a
logistic regression model with a single treatment parameter. All
analyses were executed using \texttt{R}\citep{R} within the integrated
development environmentof RStudio\citep{Rstudio}. Model convergence was
assessed by examination of the Monte Carlo Standard Error \textless{}
10\% of the posterior standard deviation, \(n_{eff}\) an estimate of the
effective number of independent draws from the posterior distribution of
the estimand \textgreater{} 10\% maximum and \(\hat{R}\) a measures the
ratio of the average variance of samples within each chain to the
variance of the pooled samples across chains \textless{} 1.1. The
statistical code can be found on Github
(https://github.com/brophyj/eCPR).

>>>>

\begin{keyword}
    extracorporeal CPR \sep 
    Bayesian statistics
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, enhanced, borderline west={3pt}{0pt}{shadecolor}, sharp corners, breakable, interior hidden, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

Posterior distributions were estimated using the Hamiltonian Monte
Carlo,a form of Markov Chain Monte Carlo simulations in which the
gradient of the log posterior is used to efficiently sample the
posterior space. This was implemented in \texttt{Stan}\citep{stan} using
the front end \texttt{rstanarm} package\citep{rstanarm} by fitting a
logistic regression model with a single treatment parameter. All
analyses were executed using \texttt{R}\citep{R} within the integrated
development environmentof RStudio\citep{Rstudio}. Model convergence was
assessed by examination of the Monte Carlo Standard Error \textless{}
10\% of the posterior standard deviation, \(n_{eff}\) an estimate of the
effective number of independent draws from the posterior distribution of
the estimand \textgreater{} 10\% maximum and \(\hat{R}\) a measures the
ratio of the average variance of samples within each chain to the
variance of the pooled samples across chains \textless{} 1.1. Reporting
has followed the Bayesian Analysis Reporting Guidelines\citep{RN6637}.
The statistical code can be found on Github
(https://github.com/brophyj/eCPR).
